---
title: "R Notebook"
output: html_notebook
---

let's load in and explore the data. What is our main data again?
```{r}
Bomb_df <- read.csv("/Users/alexandrareich/Desktop/THESIS TIME!/Compilation of GITHUB project code/BOMB_TIME/Data/Hatchery egg condition data 1-11-22_modified.csv")

names(Bomb_df)
library(tidyverse)
#View(Bomb_df)
```

Plot exploratory stuff
Interests: ED(energy density) and LIPID CONTENT vs... eg size? length? Hatch wild?
```{r}
library(ggplot2)
library(cowplot)

#the energy density
#class(Bomb_df$Wild_or_hatch)
ggplot(Bomb_df) + aes(x=Wild_or_hatch, y=BombED.Dry.) + geom_boxplot() +geom_jitter()

#the lipid content
ggplot(Bomb_df) + aes(x=Wild_or_hatch, y=X..lipid) + geom_boxplot() +geom_jitter()

```

05/02/22 addtiion: t-tests!
```{r}
?t.test
library(dplyr)
#H0: not different
#HA: Hatch < Wild

#bomb
names(Bomb_df)
Wild_egg_energy <- Bomb_df %>% 
  filter(Wild_or_hatch == "W") %>%
  select(BombED.Dry.)
    
Hatch_egg_energy <- Bomb_df %>% 
  filter(Wild_or_hatch == "H") %>%
  select(BombED.Dry.)

(T_test_ED <- t.test(Hatch_egg_energy, Wild_egg_energy, alternative="less", var.equal = T) )
##HA: x has a lower mean than y
##assuming homogeneity (constant variance... Is this true tho?)

t.test(Hatch_egg_energy, Wild_egg_energy, alternative="less", var.equal = F) 
##HA: x has a lower mean than y
##assuming homogeneity (Not assuming homogeneity)
##probs not using this one


#lipid
Wild_lipid_energy <- Bomb_df %>% 
  filter(Wild_or_hatch == "W") %>%
  select(X..lipid)
    
Hatch_lipid_energy <- Bomb_df %>% 
  filter(Wild_or_hatch == "H") %>%
  select(X..lipid)

(T_test_lipid <- t.test(Hatch_lipid_energy, Wild_lipid_energy, alternative="less", var.equal = T))


#I should probably record these t-test values in the resutls section. My results section is a work in progress...
```

Normality tests and such? 05/02/22
```{r}
names(Bomb_df)
mod_E <- aov(BombED.Dry. ~ Wild_or_hatch, data=Bomb_df)
mod_L <- aov(X..lipid ~ Wild_or_hatch, data=Bomb_df)

fitted(mod_E)
#plot residuals vs. fitted?
r_E <- resid(mod_E)
ggplot(Bomb_df) + aes(x=r_E, y=mod_E, color=Wild_or_hatch) + geom_point()
plot(resid(mod_E))
ggplot(Bomb_df) + aes(x=r_E) + geom_histogram()
qqnorm(r_E) #concave-down
shapiro.test(r_E) #shit, not normal. Normality of residuals violated. Is normality of residuals an assumption?

plot(fitted(mod_E), r_E)

#ugh! 

fit_L <- fitted(mod_L)
r_L <- resid(mod_L)
qqnorm(r_L)
shapiro.test(r_L) #yes normal, lm ok

plot(r_L) #ok weird, might be an outlier in there

library(onewaytests)
?bf.test  #use this test to test homogeneity resids!!

hist(Bomb_df$BombED.Dry.)
hist(log(Bomb_df$BombED.Dry.))

```


Tangent: 05/02/22
Normality is violated for energy density. Try a glm?
Which glm family to choose??

Or... log trasform? try transforming x first
```{r}
?glm
?box
library(car)
?boxCox
boxCox(mod_E)
#boxCox(mod_E, lambda=seq(-2, 8, 1/5)) #ugh
mod_E_log <- aov(log(BombED.Dry.) ~ Wild_or_hatch, data=Bomb_df)
mod_E_sqrt <- aov(sqrt(BombED.Dry.) ~ Wild_or_hatch, data=Bomb_df)
mod_E_recip <- aov((1/BombED.Dry.) ~ Wild_or_hatch, data=Bomb_df)

plot(resid(mod_E_log))
qqnorm(resid(mod_E_log))
qqnorm(r_E)
qqnorm(resid(mod_E_sqrt)) #none of these look good
qqnorm(resid(mod_E_recip)) #this one looks bad in the other direction

shapiro.test(resid(mod_E_recip))

```


I see more variation in the W for bomb, not so much for lipids. What does this mean?
I need to add in egg size and fish length (and maybe GSI) and see what this means!

DATA WRANGING
Goal: attach bomb data to individual.
What is the indiviudal data called?
(see main R project folder)
Go back into "Cleaned up Analysis and Graphs.rnb and create a clean csv file with the GSI, and save that locally.
```{r}
#GSI
GSI_c <- read.csv("Data/c_GSI_for_boms.csv")

#GSI clean
GSI_c_clean <- read.csv("Data/c_GSI_clean_for_bomb.csv")

#eggs
Eggs_c <- read.csv("Data/c_all_eggs_bomb.csv")
C_other_data <- read.csv("Data/c_all_other_stuff.csv")
  
  
#eggs clean
Eggs_c_clean <- read.csv("Data/c_clean_bomb.csv")

#another idea: add energy content as covariate in egg size analysis?? Uhhh...later. It's bomb time
```

Combine data frames so your bomb dataframe has covariates
```{r}
#joinby
#r_bind
#c_bind
#see data wrangling worksheet

names(Bomb_df)
Bomb_df_relevant <- Bomb_df[, c(2,3,6,7,8,9,10)]

#View(GSI_c_clean)
length(GSI_c_clean$ID)
(Bomb_df$InvestNo)
Bomb_df_relevant$ID<-Bomb_df$InvestNo
(GSI_c$ID)
#join Bomb_df_relevant with GSI_c. This will remove non-egg bearers (there were sone? and then I can remove weird fishies after)
Bomb_with_covariates <- left_join(Bomb_df_relevant, GSI_c, by = "ID" )
length(Bomb_df_relevant$InvestNo)
length(Bomb_with_covariates$ID) #woohoo, it worked

View(Bomb_with_covariates)


```

Add in the covariate of average egg size
```{r}
names(Bomb_with_covariates)
#of interest: GSI
#add in: average egg size. This exists somewhere.
#where is my average egg size document?
names(Eggs_c)
names(Eggs_c_clean)
Eggs_c_clean$Fish.ID
#test <- Eggs_c %>%
 # group_by(Fish.ID) %>%
#  select(Fish.ID, Diameter..mm.) %>%
 # mutate(EggDiam = mean(Diameter..mm.))

Eggs_av <- Eggs_c %>%
  group_by(Fish.ID) %>%
  summarize(Eggs_av = mean(Diameter..mm.))

#NICE!
#combine Eggs_av with Bomb_with_covariates
names(Bomb_with_covariates)
Bomb_with_covariates$Fish.ID
names(Eggs_av)

#join them!!
Bomb_with_covariates <- left_join(Bomb_with_covariates, Eggs_av, by = "Fish.ID" )
  
```


Bomb_with_covariates is my dataset right now. Let's check out them covariates!
(and maybe normality assuption too on the energy and lipid data!!)
Pause for now. 04/22/22. Above is what to do next.'

05/02/22
```{r}
Bomb_with_covariates_notweird <- Bomb_with_covariates %>%
  filter(Weird=="n")
Bomb_with_covariates_notweird_noNA <- na.omit(Bomb_with_covariates_notweird)
##gets rid of fish number 25, where Milo didn't record the GSI
##ok, that's my DF, the one I want to use.
```

use this dataframe: Bomb_with_covariates_notweird_noNA
Covariates of interest: 
-Egg size
-Fish length
- wild or hatch

response var:
- Energy denstiy
-Lipid conten

Potentially also:
- GSI
```{r}
names(Bomb_with_covariates_notweird_noNA)

#energy
ggplot(Bomb_with_covariates_notweird_noNA) + aes(x=Eggs_av, y=BombED.Dry., color=Wild.or.Hatch) + geom_point()
ggplot(Bomb_with_covariates_notweird_noNA) + aes(x=Length..mm., y=BombED.Dry., color=Wild.or.Hatch) + geom_point()


#lipid
ggplot(Bomb_with_covariates_notweird_noNA) + aes(x=Eggs_av, y=X..lipid, color=Wild.or.Hatch) + geom_point()
ggplot(Bomb_with_covariates_notweird_noNA) + aes(x=Length..mm., y=X..lipid, color=Wild.or.Hatch) + geom_point()

#interactions?
ggplot(Bomb_with_covariates_notweird_noNA) + aes(x=Length..mm., y=Eggs_av, color=Wild.or.Hatch) + geom_point() #ummm
```

So... there's just no diff between W and H, no matter how you look at it. Build a model for this?
```{r}

```

