---
title: "R Notebook"
output: html_notebook
---

let's load in and explore the data. What is our main data again?
```{r}
Bomb_df <- read.csv("/Users/alexandrareich/Desktop/THESIS TIME!/Compilation of GITHUB project code/BOMB_TIME/Data/Hatchery egg condition data 1-11-22_modified.csv")

names(Bomb_df)
library(tidyverse)
View(Bomb_df)
```

Plot exploratory stuff
Interests: ED(energy density) and LIPID CONTENT vs... eg size? length? Hatch wild?
```{r}
library(ggplot2)
library(cowplot)

#the energy density
#class(Bomb_df$Wild_or_hatch)
ggplot(Bomb_df) + aes(x=Wild_or_hatch, y=BombED.Dry.) + geom_boxplot() +geom_jitter()

#the lipid content
ggplot(Bomb_df) + aes(x=Wild_or_hatch, y=X..lipid) + geom_boxplot() +geom_jitter()

```

I see more variation in the W for bomb, not so much for lipids. What does this mean?
I need to add in egg size and fish length (and maybe GSI) and see what this means!

DATA WRANGING
Goal: attach bomb data to individual.
What is the indiviudal data called?
(see main R project folder)
Go back into "Cleaned up Analysis and Graphs.rnb and create a clean csv file with the GSI, and save that locally.
```{r}
#GSI
GSI_c <- read.csv("Data/c_GSI_for_boms.csv")

#GSI clean
GSI_c_clean <- read.csv("Data/c_GSI_clean_for_bomb.csv")

#eggs
Eggs_c <- read.csv("Data/c_all_eggs_bomb.csv")
C_other_data <- read.csv("Data/c_all_other_stuff.csv")
  
  
#eggs clean
Eggs_c_clean <- read.csv("Data/c_GSI_clean_for_bomb.csv")

#another idea: add energy content as covariate in egg size analysis?? Uhhh...later. It's bomb time
```

Combine data frames so your bomb dataframe has covariates
```{r}
#joinby
#r_bind
#c_bind
#see data wrangling worksheet

```

